---
title: "Percent Cover & Diversity"
author: "Jamie McDevitt-Irwin"
date: "2023-10-12"
output: html_document
---


Notes
- we removed time zero from the model because we are not interested in "slopes" 

# Packages
```{r, echo=FALSE}
library(tidyverse);library(ggplot2);library(vegan);library(zoo);library(ggpubr);library(plotly);library(ggordiplots);library(ecotraj);library(DHARMa);library(ggeffects);library(emmeans);library(indicspecies);library(lme4);library(performance);library(glmmTMB)
```

# Load Data
```{r}
load("../data/created-data/broad.df_long.RData")
load("../data/created-data/broad.df_wide.RData")
load("../data/created-data/data_long.RData")
load("../data/created-data/data_wide.RData")
load("../data/created-data/diversity.df_wide.RData")
load("../data/created-data/herbivores_long.RData")
load("../data/created-data/metadata.RData")

```


# Percent Cover
```{r}
pd <- position_dodge(0.2)

# Total algae cover
p_total.cover <-  broad.df_wide %>%
  group_by(Treatment, Time_point) %>%
  summarize(mean=mean(Total.Algae.Cover),
            sd=sd(Total.Algae.Cover),
            se=sd/sqrt(n())) %>%
  ggplot(aes(y=mean, x=Time_point, group=Treatment, colour=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax=mean+se),
                  size=1.2,
                   position=pd) +
  geom_line(alpha=0.3)+
  #facet_wrap(~Treatment) + 
  theme_pubr(base_size=16) +
    theme(axis.text.x = element_blank())+
  labs(y="Total Algae Cover (+/- SE)", 
       x= "",
       colour= "Treatment")  +
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" , "#FF9966")) 


p_total.cover 

ggsave(p_total.cover, file="../figures/total-algae-cover.png",
       height=7, width=11)





# Perennial vs ephemeral
p_perennial.vs.ephemeral <- broad.df_long %>%
  filter(Taxa %in% c("Perennial", "Ephemeral")) %>%
  filter(Time_point %in% c("Time Zero",
                           "One Month",
                           "Two Months",
                           "Three Months",
                           "Four Months",
                           "Five Months")) %>%
  group_by(Taxa, Treatment, Time_point) %>%
  summarize(mean=mean(Percent.cover),
            sd=sd(Percent.cover),
            se=sd/sqrt(n())) %>%
  ggplot(aes(y=mean, x=Time_point, 
             group= Taxa, shape=Taxa,
             colour=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax=mean+se),
                  size=1) +
  geom_line()+
  facet_wrap(~Treatment) + 
  theme_pubr(base_size=16) +
    theme(axis.text.x = element_blank())+
  labs(y="Mean Percent Cover (+/- SE)", 
       x= "Sampling Month",
       shape= "Algae")+ 
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966"))+
  scale_shape_manual(values=c(2,16))+
  guides(colour="none")

  
p_perennial.vs.ephemeral

ggsave(p_perennial.vs.ephemeral, file="../figures/perennial-vs-ephemeral.png",
       height=7, width=10)




# Plot only the abundant taxa 
abund <- data_long %>%
  group_by(Taxa) %>%
  summarize(mean=mean(Percent.cover)) %>%
  arrange(desc(mean)) %>% 
  # filter out taxa that are above 1% average cover thruoghout the whole time series 
  filter(mean > .01)

p_abundant <- data_long %>%
  filter(Taxa %in% abund$Taxa) %>%
  ggplot(aes(y=Percent.cover, x=Date, color=Taxa, fill=Taxa)) +
  geom_smooth() +
  facet_wrap(~ Treatment) + 
  theme_pubr(base_size=16)
p_abundant
ggsave(p_abundant, file="../figures/most-abundant-taxa.png",
       height=7, width=13)








# Relative Abundance
p_relabund_treatment <- data_long %>%
  # get rid of time zero 
  filter(Time_point != "Time Zero") %>%
  # only plot the most abundant taxa, put others as "other" category
  mutate(Abund.Taxa= ifelse(!Taxa %in% abund$Taxa, "Other", Taxa)) %>%
  mutate(Abund.Taxa = fct_relevel(Abund.Taxa, "Other", after = Inf)) %>%
  # group by time point, treatment and taxa
  group_by(Time_point, Treatment, Abund.Taxa) %>%
  # average over the plots
  summarize(mean=mean(Percent.cover)) %>%
  ggplot(aes(x=as.factor(Treatment), y=mean, fill=Abund.Taxa, color=Abund.Taxa)) + 
  geom_bar(aes(), stat="identity", position="fill") +
  facet_wrap(~Time_point)+
  theme_pubr()+ 
  theme(legend.position="right") +
  labs(x = "Treatment", y="Relative Abundance")  +
  theme(axis.text.x = element_text(angle = 45, hjust=1))


p_relabund_treatment

ggsave(p_relabund_treatment, file="../figures/relative-abundance.png",
       height=10, width=13)


# Shannon Diversity

p_shannon <- diversity.df_wide %>%
  #filter(Time_point != "Time Zero") %>%
  group_by(Treatment, Time_point) %>%
  summarize(mean=mean(Shannon),
            sd=sd(Shannon),
            se=sd/sqrt(n())) %>%
  ggplot(aes(y=mean, x=Time_point, group=Treatment, colour=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax=mean+se), position=pd, size=1.25) +
  geom_line(position=pd,
            alpha=0.3)+
    theme(axis.text.x = element_blank())+
  labs(y="Shannon Diversity (+/- SE)", 
       x= "Sampling Month")+
  theme_pubr(base_size=16)+
  #facet_wrap(~Treatment) +
      #theme(axis.text.x = element_blank())+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966"))+
  scale_x_discrete(labels = c("Time Zero" = "0", 
                              "One Month" = "1", 
                              "Two Months" = "2",
                              "Three Months" = "3",
                              "Four Months" = "4",
                              "Five Months" = "5",
                              "Six Months" = "6",
                              "Seven Months" = "7", 
                              "Eight Months" = "8",
                              "Nine Months" = "9",
                              "Ten Months" = "10",
                              "Eleven Months" = "11",
                              "Twelve Months" = "12"))
p_shannon


ggsave(p_shannon, file="../figures/shannon-diversity.png",
       height=7, width=13)


# all treatments show the same trend of increasing diversity except for unmanipulated, but they also show a plateau eventually 


p_fig1 <- ggarrange(p_total.cover,
          p_shannon,
          common.legend = TRUE,
          nrow=2,
          legend = "right")

p_fig1

ggsave(p_fig1, file= "../figures/figure1.png",
       height=8,
       width=10)
```






# Mixed Models
https://cran.r-project.org/web/packages/emmeans/vignettes/AQuickStart.html
https://rdrr.io/cran/emmeans/man/emtrends.html
https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html 
https://stats.stackexchange.com/questions/563765/probing-categorical-3-levels-x-continuous-var-with-emmeans



We decided to include month as a categorical factor after we ran models with it as a continuous factor and it wasn't fitting the data well because of large spikes in one month for some of the treatments. We have enough power to include it as a categorical factor and it makes more sense for evaluating this dataset. 

"The most “appropriate” choice (treating Time as a factor or a continuous variable) will depend on our goals. If we want to see WHERE changes occurred (e.g., across particular time points), then we will want to treat time as a categorical variable. If we want to see the strength of the relationship (i.e., how strongly [and linearly] related Time and MLT scores are), then we will want to treat Time as a continuous variable."
https://kristopherkyle.github.io/IntroQuantALRM/8_Linear_Mixed_Effects_Models.html



  
## Total Cover

```{r}
### Total Algae Cover ###
hist(broad.df_wide$Total.Algae.Cover)
range(broad.df_wide$Total.Algae.Cover)
str(broad.df_wide)
#  month is continuous --> but we want to run as categorical 
# treatment is categorical

unique(broad.df_wide$Time_point)

# get rid of time zero
df <- broad.df_wide %>%
  filter(Time_point != "Time Zero") %>%
  # filter(Time_point %in% c(
  #                          "One Month",
  #                          "Two Months",
  #                          "Three Months",
  #                          "Four Months",
  #                          "Five Months")) %>%
  droplevels()
str(df)
hist(df$Total.Algae.Cover)


model1 <- lmer(Total.Algae.Cover ~ 
                 as.factor(Month) * Treatment + 
                 (1|Block/Plot) , data = df)
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2)  # all significant


# Model Diagnostics 
# try the performance package
check_model(model1) # high collinearity but its two interacting categorical factors so doesn't matter https://statisticalhorizons.com/multicollinearity/ 
# looks ok!
# homogeneity of variance is a bit hump shaped
# looks better now



# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) # i think this looks ok too, large sample sizes will usually make dharma significant 

plotResiduals(res_simulated, as.factor(df$Month)) # this one looks like the biggest driver
plotResiduals(res_simulated, df$Treatment)


# EMMEANS
emmip(model1, Treatment ~ Month, cov.reduce = range)

em <- pairs(emmeans(model1, ~Treatment*as.factor(Month)), simple="Treatment")
em
# this does pairwise comparisons between levels of treatment across each month 





model <- glmmTMB(
  Total.Algae.Cover ~ as.factor(Month) * Treatment + (1|Block/Plot),
  # Data and Family (assuming your Algae Cover is approximately Normal)
  dispformula = ~ Treatment,
  data = df,
  family = gaussian(link=identity)
)

check_model(model) # looks alot better

# check against fixed effects
res_simulated <- simulateResiduals(model, plot=TRUE) # i think this looks ok too, large sample sizes will usually make dharma significant 

plotResiduals(res_simulated, as.factor(df$Month)) # this one looks like the biggest driver
plotResiduals(res_simulated, df$Treatment)


em <- pairs(emmeans(model, ~Treatment*as.factor(Month)), simple="Treatment")
em
# this does pairwise comparisons between levels of treatment across each month 


```


Try a beta distribution because we see some residual patterns and maybe modeling it this way will be better
```{r}
library(glmmTMB)

# Have to nudge the true 1's because you can't have these in a beta distribution
# https://psycnet.apa.org/record/2006-03820-004 
n_obs <- nrow(df)
df$Total.Algae.Cover_Transformed <- (df$Total.Algae.Cover * (n_obs - 1) + 0.5) / n_obs

range(df$Total.Algae.Cover_Transformed)
hist(df$Total.Algae.Cover_Transformed)



model_beta <- glmmTMB(
  Total.Algae.Cover_Transformed ~ as.factor(Month) * Treatment + (1|Block/Plot),
  data = df,
  family = beta_family(link = "logit")
)

check_model(model_beta) # looks good

# check against fixed effects
res_simulated <- simulateResiduals(model_beta, plot=TRUE) # some significance, but we do have a big N

plotResiduals(res_simulated,as.factor(df$Month)) # sig?
plotResiduals(res_simulated, df$Treatment) # sig


# Model dispersion
model_disp <- glmmTMB(
  Total.Algae.Cover_Transformed ~ as.factor(Month) * Treatment + (1|Block/Plot),
  dispformula = ~ as.factor(Month),
  data = df,
  family = beta_family(link = "logit")
)

summary(model_disp)
performance::r2(model_disp) # doesn't work becasue the model is too complex, verify model fit with AIC


model_nodisp <- glmmTMB(
  Total.Algae.Cover_Transformed ~ as.factor(Month) * Treatment + (1|Block/Plot),
  # constant dispersion
  dispformula = ~ 1,
  data = df,
  family = beta_family(link = "logit")
)

AIC(model_disp, model_nodisp) # dispersion formula is much better 

check_model(model_disp)

# check against fixed effects
res_simulated <- simulateResiduals(model_disp, plot=TRUE) # i think this looks ok too, large sample sizes will usually make dharma significant 

plotResiduals(res_simulated, as.factor(df$Month)) # this one looks like the biggest driver
plotResiduals(res_simulated, df$Treatment)

# this fits the data the best 



# ANOVA and post-hoc contrasts 
car::Anova(model_disp, type=2) # same results 

em <- pairs(emmeans(model_disp, ~Treatment*as.factor(Month)), 
            simple="Treatment",
            adjust="Tukey")
em
```
Over time, always caged, unamnipulated control  have a decrease in algae cover. Whereas always uncaged and the cage control have an increase in algae cover. Caged for one month stays relatively the same (basically what we are seeing in the raw data plots).





## Diversity
```{r}
### Species Diversity ###
hist(diversity.df_wide$Shannon)

df <- diversity.df_wide %>%
  filter(Time_point != "Time Zero") %>%
  # filter(Time_point %in% c("Time Zero",
  #                          "One Month",
  #                          "Two Months",
  #                          "Three Months",
  #                          "Four Months",
  #                          "Five Months",
  #                          "Six Months")) %>%
  droplevels()

model1_diversity <- lmer(Shannon ~ as.factor(Month) * Treatment + (1|Block/Plot), data = df)


summary(model1_diversity)
performance::r2(model1_diversity)

car::Anova(model1_diversity, type=2) # interaction is not sig

model2_diversity <- lmer(Shannon ~ as.factor(Month) + Treatment + (1|Block/Plot), data = df)

performance::r2(model2_diversity)


car::Anova(model2_diversity, type=2) # only month is significant

# Model Diagnostics 
performance::check_model(model2_diversity) # looks amazing :)

# check against fixed effects
res_simulated <- simulateResiduals(model2_diversity, plot=TRUE) # some significance, but we do have a big N

plotResiduals(res_simulated,as.factor(df$Month)) # ok
plotResiduals(res_simulated, df$Treatment) # ok




#  EMMEANS
emmip(model2_diversity, ~as.factor(Month), cov.reduce = range)

# didn't report because we aren't interested in this
pairs(emmeans(model2_diversity, ~as.factor(Month)),adjust="Tukey")

```
