---
title: "ETA"
author: "Jamie McDevitt-Irwin"
date: "2023-10-12"
output: html_document
---



# Packages
```{r, echo=FALSE}
library(tidyverse);library(ggplot2);library(vegan);library(zoo);library(ggpubr);library(plotly);library(ggordiplots);library(ecotraj);library(DHARMa);library(ggeffects);library(emmeans);library(indicspecies);library(lme4);library(performance)
```


# Load Data
```{r}
load("../data/created-data/broad.df_long.RData")
load("../data/created-data/broad.df_wide.RData")
load("../data/created-data/data_long.RData")
load("../data/created-data/data_wide.RData")
load("../data/created-data/diversity.df_wide.RData")
load("../data/created-data/herbivores_long.RData")
load("../data/created-data/metadata.RData")

```

# 12 Months


https://emf-creaf.github.io/ecotraj/articles/IntroductionETA.html
Be careful with CTA because the order of the different treatments isn't the same by subsetted dataset. 
They dont suggest square rooting your bray analysis.

## Overall
```{r}
# CTA Analysis
# average all the percent cover data by treatment and time point
colnames(data_wide)

cta.data <- data_wide %>%
  group_by(Time_point, Treatment) %>%
  # average our taxa for each time point and treatment (across plots)
    summarise_at(vars(Bare.rock:Eggs), mean, na.rm = TRUE) %>%
  droplevels()

dim(cta.data) # 65 plots (not 66 because we missed sampling one plot once )

# Prep the data
sites= cta.data$Treatment
surveys= cta.data$Time_point
#D= dist(cta.data[3:28]) # here we are just using euclidian distance (length of a line segment between two points)
#is.metric(D) # TRUE (yes because its euclidean)

# test out bray
colnames(cta.data)
D <- vegan::vegdist(cta.data[3:31], "bray")
x <- defineTrajectories(D, sites) # surveys only needed if sites are not in order



is.metric(D) # TRUE, so wouldn't need to do any transformation for CTA
# seems to be fine then! we can  use bray-curtis 

# check the order for the legend
levels(cta.data$Treatment)

pdf(file="../figures/cta.pdf", height=8, width=11)

trajectoryPCoA(x, traj.colors =c("#006699", "#CC33CC", "#FF99FF","#009999","#FF9966"),lwd=4)
legend("topleft", col=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966"),
       legend=c("Always caged", 
                "Always uncaged", 
                "Cage control", 
                "Caged for one month",
                "Unmanipulated control"), 
       bty="n", lty=1, lwd = 2)

dev.off()


trajectoryLengths(x)
# total length pathway
# always caged has the longest total pathway, always uncaged has teh lowest total pathway
# you can see huge trajectory lengths early on for caged treatments
# summing up the whole path you see that always caged and caged for one month have the longest pathways 
 
trajectoryAngles(x)
# caged for one month has the greatest angles then always uncaged
# always caged and unmanipulated control and cage contorl have the lowest angles 


trajectoryDirectionality(x) #overall directionality of a ecosystem trajectory (i.e. if the pathway consistently follows the same direction in Ω
# unmanpulated control has the lowest directionality, always uncaged and cage control have the highest


trajectoryConvergence(x) # The function performs the Mann-Whitney trend test. Values of the statistic (‘tau’) larger than 0 correspond to trajectories that are diverging, whereas values lower than 0 correspond to trajectories that are converging. 
# Diverging:unanipulated control and always caged, unmanipulated control and always uncaged, unmanpulated control and caged forone month
# nothing really interesting? 


trajectoryInternalVariation(x)
# internal variation of tates within each trajectory
# more curved == lower inernal variation
# can see caged for one month is really high at ss_2
```



## By Plot
```{r}
# Run these on the entire dataset for the plot level
str(data_wide)
dim(data_wide)

# get rid of plot 35 that is missing a time point
cta_data <- data_wide %>%
  filter(!Plot == "35") %>%
  droplevels()
dim(cta_data)

# Prep the data
sites= cta_data$Plot
surveys= cta_data$Time_point
colnames(cta_data)
D = vegan::vegdist(cta_data[8:36], "bray")
is.metric(D) # TRUE

# Define trajectories
unique(surveys)
x <- defineTrajectories(D, sites) # surveys only needed if sites are not in order


# Get plot level values
lengths <- trajectoryLengths(x) # we want Path = total path length
#View(lengths)

angles <- trajectoryAngles(x) # we want mean = mean angles
#View(angles)

directionality <- as.data.frame(trajectoryDirectionality(x))


#View(directionality)
# Add these back to metadata
cta.metadata <- metadata %>%
  filter(!Plot == "35") %>%
  droplevels()


cta.full.df <- left_join(cta.metadata, 
                         rownames_to_column(lengths), by=c("Plot"="rowname")) %>%
  left_join(rownames_to_column(angles), 
            by=c("Plot"="rowname")) %>%
  left_join(rownames_to_column(directionality), 
            by=c("Plot"="rowname")) %>%
  rename("directionality"= "trajectoryDirectionality(x)") %>%
  rename(Total.Path.Length = Path) %>%
  rename(Mean.Angles = mean)

colnames(cta.full.df)

#View(cta.full.df)
# i think we are interested in trajectory, mean and directionality
#mean =angesl

# Trajectory length
# the total pathway length 
p_traj_lengths <- cta.full.df %>%
  ggplot(aes(x=Treatment, y=Total.Path.Length, color=Treatment)) +
  geom_boxplot() +
  geom_jitter(size=2)+
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Lengths")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", "#009999", "#FF9966"))+
  ggtitle("a)")
# Shows that always caged, caged for one month  have the longest trajectories? have the biggest changes over months? 
p_traj_lengths




# Angles
p_traj_angles <- cta.full.df %>%
  ggplot(aes(x=Treatment, y=Mean.Angles, colour=Treatment)) +
geom_boxplot() +
  geom_jitter(size=2)+
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Angles")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", "#009999", "#FF9966"))+
  ggtitle("a)")
# always uncaged, caged for one month and unmanipulated have the biggest angles (biggest switches in directions?)

p_traj_angles

# Directionality
p_traj_direction <- cta.full.df %>%
  ggplot(aes(x=Treatment, y=directionality, colour=Treatment)) +
  geom_boxplot()+
  geom_jitter(size=2)+
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Directionality")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", "#009999","#FF9966"))+ ggtitle("b)")
# always caged and unmanipulated have the lowest directionality 
#overall directionality of a ecosystem trajectory (i.e. if the pathway consistently follows the same direction in Ω
p_traj_direction
 
```



### Trajectory Length
```{r}
str(cta.full.df)
hist(cta.full.df$Total.Path.Length)
range(cta.full.df$Total.Path.Length) # all positive, continuous
dim(cta.full.df) # 59 plots because we had to exclude one 

# Total Length Pathway
model1 <- lmer(Total.Path.Length ~ Treatment + (1|Block), data = cta.full.df)
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2) # significant

check_model(model1) # looks good

# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) # some significance, but we do have a big N

plotResiduals(res_simulated, cta.full.df$Treatment) # ok



emmip(model1, ~ Treatment) #always caged, caged for one month have the longest trajectories


EMM <- emmeans(model1, "Treatment")
EMM
pairs(EMM, adjust="Tukey")
# always caged vs uncaged
# always caged vs cage control
# always caged vs unmanipulated
# always uncaged vs caged for one month


p_emmeans_lengths <- as.data.frame(EMM) %>%
  ggplot(aes(x=Treatment, y=emmean, colour=Treatment)) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), size=1.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Length (emmean +/- 95% CI)")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                               "#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", 
                             "#009999","#FF9966"))+
  ggtitle("a)")
p_emmeans_lengths 
```



### Angles
```{r}
str(cta.full.df)
hist(cta.full.df$Mean.Angles)
range(cta.full.df$Mean.Angles) # all positive, continuous
dim(cta.full.df) # 59 plots because we had to exclude one 


# Angles
model1 <- lmer(Mean.Angles ~ Treatment + (1|Block), data = cta.full.df) 
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2) # significant

check_model(model1) # loooks ok enough

# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) # some significance, but we do have a big N

plotResiduals(res_simulated, cta.full.df$Treatment) # ok



emmip(model1, ~ Treatment) # unmanipulated control, caged for one montha and always uncaged have the largest angles
EMM <- emmeans(model1, "Treatment")
EMM
pairs(EMM, adjust="Tukey")




p_emmeans_angles <- as.data.frame(EMM) %>%
  ggplot(aes(x=Treatment, y=emmean, colour=Treatment)) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), size=1.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Angle (emmean +/- 95% CI)")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                               "#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", 
                             "#009999","#FF9966"))+
  ggtitle("b)")
p_emmeans_angles
```





### Directionality
```{r}
str(cta.full.df)
hist(cta.full.df$directionality)
range(cta.full.df$directionality) # all positive, continuous
dim(cta.full.df) # 59 plots because we had to exclude one 


# Directionality
model1 <- lmer(directionality ~ Treatment + (1|Block), data = cta.full.df)
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2) # significant

check_model(model1) # homogeneity of variance is not great? but maybe ok? its a small sample size
# plot #2 does seem to be an outlier at 0.7

# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) 

plotResiduals(res_simulated, cta.full.df$Treatment) # ok



emmip(model1, ~ Treatment) # always uncaged and cage control have the highest directionality
EMM <- emmeans(model1, "Treatment")
EMM
pairs(EMM, adjust="Tukey")

p_emmeans_direction <- as.data.frame(EMM) %>%
  ggplot(aes(x=Treatment, y=emmean, colour=Treatment)) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), size=1.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Directionality (emmean +/- 95% CI)")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                               "#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", 
                             "#009999","#FF9966"))+
  ggtitle("c)")
p_emmeans_direction


# Try the model without the outlier and see if it fits better
test <- cta.full.df %>%
  filter(!directionality > 0.7)
model1 <- lmer(directionality ~ Treatment + (1|Block), data = test)

performance::r2(model1)  
car::Anova(model1, type=2) # significant

check_model(model1) # better without this outlier

emmip(model1, ~ Treatment) # always uncaged and cage control have the highest directionality
EMM <- emmeans(model1, "Treatment")
EMM
pairs(EMM, adjust="Tukey")
# same qualitative result
# so report the results above with the outlier included
```


```{r}
p_emmean_all <- ggarrange(p_emmeans_lengths,
          p_emmeans_angles,
          p_emmeans_direction,
          common.legend=TRUE,
          ncol=3)
p_emmean_all
ggsave(p_emmean_all, file="../figures/emmeans-eta.png",
       height=6, width=11)
```




# Five Months


Replicated on the five month data, prior to herbivores increasing in the cages. This will go in the supplement.

## Overall
```{r}
# CTA Analysis
# average all the percent cover data by treatment and time point
colnames(data_wide)

cta.data <- data_wide %>%
  # filter to only five months
   filter(Time_point %in% c("Time Zero",
                           "One Month",
                           "Two Months",
                           "Three Months",
                           "Four Months",
                           "Five Months")) %>%
  group_by(Time_point, Treatment) %>%
  # average our taxa for each time point and treatment (across plots)
    summarise_at(vars(Bare.rock:Eggs), mean, na.rm = TRUE) %>%
  droplevels()

dim(cta.data) # 65 plots (not 66 because we missed sampling one plot once )

# Prep the data
sites= cta.data$Treatment
surveys= cta.data$Time_point
#D= dist(cta.data[3:28]) # here we are just using euclidian distance (length of a line segment between two points)
#is.metric(D) # TRUE (yes because its euclidean)

# test out bray
colnames(cta.data)
D <- vegan::vegdist(cta.data[3:31], "bray")
x <- defineTrajectories(D, sites) # surveys only needed if sites are not in order



is.metric(D) # TRUE, so wouldn't need to do any transformation for CTA
# seems to be fine then! we can  use bray-curtis 

# check the order for the legend
levels(cta.data$Treatment)

pdf(file="../figures/cta.pdf", height=8, width=11)

trajectoryPCoA(x, traj.colors =c("#006699", "#CC33CC", "#FF99FF","#009999","#FF9966"),lwd=4)
legend("topleft", col=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966"),
       legend=c("Always caged", 
                "Always uncaged", 
                "Cage control", 
                "Caged for one month",
                "Unmanipulated control"), 
       bty="n", lty=1, lwd = 2)

dev.off()


trajectoryLengths(x)
# total length pathway
# always caged has the longest total pathway, always uncaged has teh lowest total pathway
# you can see huge trajectory lengths early on for caged treatments
# summing up the whole path you see that always caged and caged for one month have the longest pathways 
 
trajectoryAngles(x)
# caged for one month has the greatest angles then always uncaged
# always caged and unmanipulated control and cage contorl have the lowest angles 


trajectoryDirectionality(x) #overall directionality of a ecosystem trajectory (i.e. if the pathway consistently follows the same direction in Ω
# unmanpulated control has the lowest directionality, always uncaged and cage control have the highest


trajectoryConvergence(x) # The function performs the Mann-Whitney trend test. Values of the statistic (‘tau’) larger than 0 correspond to trajectories that are diverging, whereas values lower than 0 correspond to trajectories that are converging. 
# Diverging:unanipulated control and always caged, unmanipulated control and always uncaged, unmanpulated control and caged forone month
# nothing really interesting? 


trajectoryInternalVariation(x)
# internal variation of tates within each trajectory
# more curved == lower inernal variation
# can see caged for one month is really high at ss_2
```



## By Plot
```{r}
# Run these on the entire dataset for the plot level
str(data_wide)
dim(data_wide)

# get rid of plot 35 that is missing a time point
cta_data <- data_wide %>%
  filter(!Plot == "35") %>%
   filter(Time_point %in% c("Time Zero",
                           "One Month",
                           "Two Months",
                           "Three Months",
                           "Four Months",
                           "Five Months")) %>%
  droplevels()
dim(cta_data)

# Prep the data
sites= cta_data$Plot
surveys= cta_data$Time_point
colnames(cta_data)
D = vegan::vegdist(cta_data[8:36], "bray")
is.metric(D) # TRUE

# Define trajectories
unique(surveys)
x <- defineTrajectories(D, sites) # surveys only needed if sites are not in order


# Get plot level values
lengths <- trajectoryLengths(x) # we want Path = total path length
#View(lengths)

angles <- trajectoryAngles(x) # we want mean = mean angles
#View(angles)

directionality <- as.data.frame(trajectoryDirectionality(x))


#View(directionality)
# Add these back to metadata
cta.metadata <- metadata %>%
  # get rid of plot 35 that we are missing
  filter(!Plot == "35") %>%
  droplevels()


cta.full.df <- left_join(cta.metadata, 
                         rownames_to_column(lengths), by=c("Plot"="rowname")) %>%
  left_join(rownames_to_column(angles), 
            by=c("Plot"="rowname")) %>%
  left_join(rownames_to_column(directionality), 
            by=c("Plot"="rowname")) %>%
  rename("directionality"= "trajectoryDirectionality(x)") %>%
  rename(Total.Path.Length = Path) %>%
  rename(Mean.Angles = mean)

colnames(cta.full.df)

#View(cta.full.df)
# i think we are interested in trajectory, mean and directionality
#mean =angesl

# Trajectory length
# the total pathway length 
p_traj_lengths <- cta.full.df %>%
  ggplot(aes(x=Treatment, y=Total.Path.Length, color=Treatment)) +
  geom_boxplot() +
  geom_jitter(size=2)+
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Lengths")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", "#009999", "#FF9966"))+
  ggtitle("a)")
# Shows that always caged, caged for one month  have the longest trajectories? have the biggest changes over months? 
p_traj_lengths

ggsave(p_traj_lengths, file="../figures/trajectory-lengths.png",
       height=7, width=10)






# Angles
p_traj_angles <- cta.full.df %>%
  ggplot(aes(x=Treatment, y=Mean.Angles, colour=Treatment)) +
geom_boxplot() +
  geom_jitter(size=2)+
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Angles")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", "#009999", "#FF9966"))+
  ggtitle("a)")
# always uncaged, caged for one month and unmanipulated have the biggest angles (biggest switches in directions?)



# Directionality
p_traj_direction <- cta.full.df %>%
  ggplot(aes(x=Treatment, y=directionality, colour=Treatment)) +
  geom_boxplot()+
  geom_jitter(size=2)+
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Directionality")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF","#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", "#009999","#FF9966"))+ ggtitle("b)")
# always caged and unmanipulated have the lowest directionality 
#overall directionality of a ecosystem trajectory (i.e. if the pathway consistently follows the same direction in Ω
p_traj_direction


ggsave(p_traj_direction, file="../figures/trajectory-directionality.png",
       height=7, width=10)

```



### Trajectory Length
```{r}
str(cta.full.df)
hist(cta.full.df$Total.Path.Length)
range(cta.full.df$Total.Path.Length) # all positive, continuous
dim(cta.full.df) # 59 plots because we had to exclude one 

# Total Length Pathway
model1 <- lmer(Total.Path.Length ~ Treatment + (1|Block), data = cta.full.df)
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2) # significant

check_model(model1) # looks good

# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) # ok

plotResiduals(res_simulated, cta.full.df$Treatment) # ok



emmip(model1, ~ Treatment) #always caged, caged for one month have the longest trajectories


EMM <- emmeans(model1, "Treatment")
EMM
pairs(EMM, adjust="Tukey")
# always caged vs uncaged
# always caged vs cage control
# always caged vs unmanipulated
# always uncaged vs caged for one month


p_emmeans_lengths_five <- as.data.frame(EMM) %>%
  ggplot(aes(x=Treatment, y=emmean, colour=Treatment)) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), size=1.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Length (emmean +/- 95% CI)")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                               "#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", 
                             "#009999","#FF9966"))+
  ggtitle("a)")
p_emmeans_lengths_five 
```



### Angles
```{r}
str(cta.full.df)
hist(cta.full.df$Mean.Angles)
range(cta.full.df$Mean.Angles) # all positive, continuous
dim(cta.full.df) # 59 plots because we had to exclude one 


# Angles
model1 <- lmer(Mean.Angles ~ Treatment + (1|Block), data = cta.full.df) 
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2) # not significant

check_model(model1) # loooks ok enough

# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) # ok

plotResiduals(res_simulated, cta.full.df$Treatment) # ok



emmip(model1, ~ Treatment) # unmanipulated control, caged for one montha and always uncaged have the largest angles
EMM <- emmeans(model1, "Treatment")
# not sig, so no posthoc contrasts



p_emmeans_angles_five <- as.data.frame(EMM) %>%
  ggplot(aes(x=Treatment, y=emmean, colour=Treatment)) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), size=1.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Angle (emmean +/- 95% CI)")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                               "#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", 
                             "#009999","#FF9966"))+
  ggtitle("b)")
p_emmeans_angles_five
```





### Directionality
```{r}
str(cta.full.df)
hist(cta.full.df$directionality)
range(cta.full.df$directionality) # all positive, continuous
dim(cta.full.df) # 59 plots because we had to exclude one 


# Directionality
model1 <- lmer(directionality ~ Treatment + (1|Block), data = cta.full.df)
summary(model1)
performance::r2(model1)  
car::Anova(model1, type=2) # not significant

check_model(model1) # all good

# check against fixed effects
res_simulated <- simulateResiduals(model1, plot=TRUE) 

plotResiduals(res_simulated, cta.full.df$Treatment) # ok



emmip(model1, ~ Treatment) # always uncaged and cage control have the highest directionality
EMM <- emmeans(model1, "Treatment")
# not sig so no posthoc contrasts

p_emmeans_direction <- as.data.frame(EMM) %>%
  ggplot(aes(x=Treatment, y=emmean, colour=Treatment)) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), size=1.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x=element_blank())+
  labs(y="Trajectory Directionality (emmean +/- 95% CI)")+
  scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                               "#009999" ,"#FF9966")) +
  scale_fill_manual(values=c("#006699", "#CC33CC","#FF99FF", 
                             "#009999","#FF9966"))+
  ggtitle("c)")
p_emmeans_direction


# Try the model without the outlier adn see if it fits better
test <- cta.full.df %>%
  filter(!directionality > 0.7)
model1 <- lmer(directionality ~ Treatment + (1|Block), data = test)

performance::r2(model1)  
car::Anova(model1, type=2) # not significant

check_model(model1) # better without this outlier

emmip(model1, ~ Treatment) # always uncaged and cage control have the highest directionality
EMM <- emmeans(model1, "Treatment")

# same qualitative result
# so report the results above with the outlier included
```


```{r}
p_emmean_all <- ggarrange(p_emmeans_lengths,
          p_emmeans_angles,
          p_emmeans_direction,
          common.legend=TRUE,
          ncol=3)
p_emmean_all 

ggsave(p_emmean_all, file="../figures/emmeans-eta.png",
       height=6, width=11)
```
