---
title: "02d.herbivores"
author: "Jamie McDevitt-Irwin"
date: "2026-01-14"
output: html_document
---


Note
- keeping all consumers, even whelk which is not a herbivore (all the rest are herbivores in some way), because even though algae are the main group, there are other taxa as well (e.g., barnacles)

# Packages
```{r, echo=FALSE}
library(tidyverse);library(ggplot2);library(vegan);library(zoo);library(ggpubr);library(plotly);library(ggordiplots);library(ecotraj);library(DHARMa);library(ggeffects);library(emmeans);library(indicspecies);library(lme4)
```


# Load Data
```{r}
load("../data/created-data/broad.df_long.RData")
load("../data/created-data/broad.df_wide.RData")
load("../data/created-data/data_long.RData")
load("../data/created-data/data_wide.RData")
load("../data/created-data/diversity.df_wide.RData")
load("../data/created-data/herbivores_long.RData")
load("../data/created-data/metadata.RData")

```




# Data Cleaning
```{r}
consumers_long.2 <- herbivores_long %>%
  mutate(Caged.YN = ifelse(Treatment == "Always caged", "Y",
                           ifelse(Treatment == "Caged for one month" & 
                                    Time_point == "One Month", "Y", "N")))

# reorder time points levels
consumers_long.2$Time_point <- factor(consumers_long.2$Time_point,
                               levels=c("Pre",
                                 "One Month", 
                                        "Two Months", 
                                        "Three Months", 
                                        "Four Months", 
                                        "Five Months", 
                                        "Six Months", 
                                        "Seven Months", 
                                        "Eight Months",
                                        "Nine Months",
                                        "Ten Months",
                                        "Eleven Months",
                                        "Twelve Months"))
  
```


# Standardize by sampling area
- this is because our cages surveyed a greater area than all others since we surveyed beyond the quadrat (so more likely to get consumers)

25cm X 25cm = 625cm2 (full cage area)
20cm X 20cm = 400cm2 (quadrat area)
```{r}

consumers_long.stand <- consumers_long.2 %>% 
  mutate(Count.corrected = case_when(
    # Condition 1: One Month + Caged for one month
    Time_point == "One Month" & Treatment == "Caged for one month" ~ Count / 625,
    
    # Condition 2: Always caged + Pre/Post
    Treatment == "Always caged" & Time_point %in% c("Pre", "Post") ~ Count / 400,
    
    # Condition 3: Always caged (other time points)
    Treatment == "Always caged" ~ Count / 625,
    
    # Default: Everything else
    TRUE ~ Count / 400
  )) %>%
  select(-Count) %>%
  mutate(Count.corrected.400cm2= Count.corrected*400)

  
consumers_wide.stand <- consumers_long.stand %>%
  pivot_wider(names_from=Taxa, 
              values_from = Count.corrected.400cm2, 
              values_fill = list(Value = 0))
```



# Summaries
```{r}
# What are the most common consumers within our experimental plots?
consumers_long.stand %>%
  # filter out dates we aren't interested in 
  filter(!Time_point == "NA") %>%
  group_by(Taxa) %>%
  summarize(mean=mean(Count.corrected.400cm2)) %>%
  arrange(desc(mean))
# most abundant is limpet and then tegula
```


# Plots
```{r}
consumers.treatment <- consumers_long.stand  %>%
  # filter out NA time points
    filter(Time_point != "Pre")  %>%
  # sum up consumers in each plot and treatment
  group_by(Time_point, Treatment, Plot) %>%
  summarize(sum=sum(Count.corrected.400cm2)) %>%
  # average over each plot 
  group_by(Time_point, Treatment) %>%
  summarize(mean=mean(sum),
            sd=sd(sum),
            se=sd/sqrt(n())) %>%
  ggplot(aes(x=Treatment, y=mean, col=Treatment)) +
  geom_pointrange(aes(ymin= mean-se, ymax= mean+se)) +
  facet_wrap(~Time_point) +
    scale_colour_manual(values=c("#006699", "#CC33CC","#FF99FF",
                                 "#009999" ,"#FF9966")) +
  theme_pubr(base_size=16) +
  labs(y="Mean Consumer Density +/- (SE) per 400 cm2") +
    theme(axis.text.x = element_blank())

consumers.treatment
  
ggsave(consumers.treatment, file="../figures/consumers.treatment.png", width=10, height=8)

```

# Pre data
```{r}
consumers_long.stand %>%
  filter(Time_point == "Pre") %>%
# sum up consumers in each plot and treatment
  group_by(Time_point, Plot) %>%
  summarize(sum=sum(Count.corrected.400cm2)) %>%
  # average over each plot 
  group_by(Time_point) %>%
  summarize(mean=mean(sum),
            sd=sd(sum),
            se=sd/sqrt(n()))
# average of 4.82 per 400cm2 
  
```
